State of the Practice for Medical Imaging Software

### 2022-10-12 StateOfPractice/Papers/MedImageSoft_SOP-arXiv/MedImageSoft_SOP_AcademicRadiology.tex
Minor edit to SOP for MI

\subsection{Recommendations on Choosing A Tech Stack}
\label{sec_recommendations_tech_stack}

A tech stack refers to a set of technologies used by a team to build software
and manage the project. Section~\ref{painpoints} lists the advantages and
disadvantages between native and web applications. We give further suggestions
on the choice of a tech stack to improve the four priority factors identified by
developers: compatibility, maintainability, performance and security.  The
suggestions are intended to provide ideas and avenues for exploration; not all
of the suggestions will be the right fit for all projects and all teams.

@@

\item \textbf{Use git and GitHub.} As mentioned in
Section~\ref{sec_score_maintainability}, almost all of the 29 MI software
projects used git, and the majority of them used GitHub. We found from the
projects' websites and our interviews with developers that, some projects moved
from other version control tools to git and GitHub. GitHub provides convenient
repository and project management, and OSS projects tend to receive more
attention and contributions on GitHub.

@@

\item \textbf{Web transmission may diminish security.} Transferring sensitive
data online can be a problem for projects requiring high security. Regulations
for some MI applications may forbid doing web transmissions. In this case, a web
application with a backend may not be an option.

>>>>

\subsection{Move To Web Applications}
\label{sec_recommendations_tech_stack}

A tech stack refers to a set of technologies used by a team to build software
and manage the project. Section~\ref{painpoints} lists the advantages and
disadvantages between native and web applications. We give further suggestions
on the choice of a tech stack to improve the four priority factors identified by
developers: compatibility, maintainability, performance, and security.  The
suggestions are intended to provide ideas and avenues for exploration; not all
of the suggestions will be the right fit for all projects and all teams.

@@

@@

\item \textbf{Web transmission may diminish security.} Transferring sensitive
data on-line can be a problem for projects requiring high security. Regulations
for some MI applications may forbid doing web transmissions. In this case, a web
application with a backend may not be an option.
